Grade Distribution Among Genders

### 2024-02-12 outputs/paper/paper.qmd
update readme

classes_dta |>
  filter(consider_regrade != "No") |>
  rename("Count" = n, "Number of Classes" = num_class, "Consider Regrade" = consider_regrade)

head(classes_dta, 10) |>
  kable(
    col.names = c("Number of Classes", "Gender", "Consider Regrade", "Count", "Percentage"),
    booktabs = TRUE,
    align = c("c", "c", "c", "c", "c")
  )

classes_dta |>
ggplot(aes(x = num_class, y = Percentage, fill = Gender)) + 
  geom_bar(stat="identity", position = "dodge") +
  theme_minimal() +
  theme(legend.key.size = unit(0.5, 'cm')) +
  geom_text(aes(label=Percentage), position=position_dodge(width=0.9), vjust=-0.25) +
  labs(x = "Classes",
       y = "Distribution by gender (percent)") +
  scale_fill_manual(values = c("Male" = "#4B659D", "Female" = "#A83B48")) +
  scale_x_discrete(labels = c("0 class", "1 class", "2 classes", "3 classes", "4 classes", "5+ classes"))

>>>>

classes_dta |>
  filter(consider_regrade != "No") |>
  rename("Count" = n, "Number of Classes" = num_class, "Consider Regrade" = consider_regrade)
head(classes_dta, 10) |>
  kable(
    col.names = c("Number of Classes", "Gender", "Consider Regrade", "Count", "Percentage"),
    booktabs = TRUE,
    align = c("c", "c", "c", "c", "c")
  )

classes_dta |>
filter(consider_regrade != "No") |>
ggplot(aes(x = num_class, y = Percentage, fill = Gender)) + 
  geom_bar(stat="identity", position = "dodge") +
  theme_minimal() +
  theme(legend.key.size = unit(0.5, 'cm')) +
  geom_text(aes(label=Percentage), position=position_dodge(width=0.9), vjust=-0.25) +
  labs(x = "Classes",
       y = "Distribution by gender (percent)") +
  scale_fill_manual(values = c("Male" = "#4B659D", "Female" = "#A83B48")) +
  scale_x_discrete(labels = c("0 class", "1 class", "2 classes", "3 classes", "4 classes", "5+ classes"))
